---
title: "icager vignette"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hello}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(kableExtra)
```

```{r setup}
library(icager)
```

# Dataset

A dataset of choices made by sample agents performing probabilistic reversal learning task. Includes actions /visits/ performed by 3 random agents, first 10 per each of 11 experimental stages.


```{r print data}
data(dx)
#For info call ?dx
```

# Import data

`import()` imports all experimentals files stored in given directories, parses on the basis on prespecified format and returns a list.

```{r import data, eval=FALSE}
mydata <- 
  import(
    list.files(
      path = choose.dir(),
      full.names = T), 
    version = 1) %>% 
  dplyr::bind_rows()
```

# Experimental scheme

An experimental scheme corresponds to probabilistic reversal learning task, in which assignment between proposed options and probabilities of access to reward are steadily reversed. An option is called a `corner`, probability of reward - reward probability (`rp`).
Each such assignment is a state of all the `corner`s' `rp` at a current moment and refered to as `contingency`. To add the contingency state, also termed as experimental phase call `contingencise()` on a dataset. Then see the data-based experimental scheme with `printscheme()`. 

Various contingencies may belong to different categories of experimental scheme, e.x. module of adaptation consists of contingencies labelled as "0x0.9" or/and "0x0", whereas the reversals stage of "0x0.3x0.9" or/and "0.3x0.9". To assign the module info use `schematize()`.

Please note that all needed defaults are set internally (values on `schematize(help=TRUE)`). For additional info call `?schematize`.

## Assign contingency

```{r assign continency}
dx <- contingencise(dx)
```

```{r}
unique(dx$contingency)
```

## Assign module

```{r assign module}
dx <- schematize(dx)
```

```{r}
with(dx, {table(info, contingency)})
```

## Print scheme

```{r eval=F}
printscheme(dx)
```

```{r exp scheme, echo = F}
printscheme(dx) %>% knitr::kable(format = "html") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

```{r hidden plot}
plotscheme(dx)
```
