---
title: "icager vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hello}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
library(dplyr)
library(icager)
#library(kableExtra)
```

```{r setup}
```

## Sample dataset

The presented dataset consists of choices made by sample agents performing probabilistic reversal learning task. It includes actions /visits/ performed by 3 random agents, first 10 per each of 11 experimental contingencies.


```{r print data}
data(dx)
```

## Import data

`import()` imports all experimentals files stored in a given directory, parses on the basis on a default format and returns a list. Different settings can be provided as a list to the `.list.form` argument. If the software version is known providing the `.version` makes the import faster.

```{r import data, eval=FALSE}
mydata <- icager::import(.version = 1) %>%
          dplyr::bind_rows()
```

If uncertain call `?digform`.

### Shortcut

`simple()` function call all the bare neccessities with defaults to provide easily ready to use complete dataset (import, bind, check for duplicated rows, standardise and assign contingency).

```{r eval=FALSE}
mydata <- simple()
```


## Inform formatting

This function help decode the data if initial software settings
are long gone. The `hint()` provides help to decode markings.

```{r}
hint(dx)
```

## Identify dataset

The `specify()` gives basic description of provided dataset.

```{r}
specify(dx)
```

## Experimental scheme

The applied here experimental scheme corresponds to probabilistic reversal learning task*, in which assignment between proposed options and probabilities of access to reward are steadily reversed. An option is called a `corner` and assigned to it probability of reward - reward probability (`rp`). The value denotes chances of 
inner doors, barring access to a bottle, to get opened. Each such assignment is a state of all the `corner`s' `rp` at a current moment and is refered to as `contingency`. To add the contingency states, also termed as experimental phases call `contingencise(data)` on a dataset. To easily visualise it call `printscheme(data)`. 

*It bases on the assumption that a change in value of a current corner's `condition` denotes start of a new contingency. Thus it would suit any procedure with scheme changes based on corner's `condition` values.

### Assign contingency

```{r assign continency}
dx <- contingencise(dx)
```

The optionally provided `metadata` argument ought to contain assignment of reward probability <num> to 
markings present in data <chr>. If uncertain call `?digcondition`, `digcondition()` and/or `hint(data)$hint`. 

```{r}
unique(dx$contingency)
```

Plase note that the division to contingencies is based solely on the actual choices so the user-set
start and finish of them are unknown. They also do not neccessarilly overlap subsequent ones.

```{r eval=F}
printscheme(dx)
```

```{r exp scheme, echo = F}
printscheme(dx) %>% knitr::kable(format = "html") %>%
   kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

Various contingencies may belong to different categories of experimental scheme, e.x. module of adaptation consists of contingencies labelled as "0x0.9" or/and "0x0", whereas the reversals stage of "0x0.3x0.9" or/and "0.3x0.9". As each experiment varies in scheme a such assignment could not be done automatically and the `specify()` function is deprecated.

### Visualise scheme

The plot presents an abstract representation of experimental scheme. Numbers in boxes denote contingency duration in hours; on the x axis contingency, on y corner number.

```{r shown plot, comment=F, warning=F, fig.dim=c(4,1.2)}
plotit(dx)
```
